Long groovy title goes here

### 2013-06-25 shanghai.tex
Moved \bar from text to commands

\newcommand{\cdef}[1]{{{\color{cyan}#1}\index{#1}}} 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-2pt\textbf{m},#1}}
\newcommand{\GN}[1]{\textswab{#1}}
\newcommand{\bGN}[1]{{\bar{\textswab{#1}}}}
\newcommand{\TT}{\underline{T}}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\cs}[1]{{\mathcal{#1}}}
\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
\newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
\newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
\newcommand{\CSbiso}[1]{\CS_0(#1)_{/\text{iso}}}
\newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}

@@

\newcommand{\tighttimes}{\hskip-1pt\times\hskip-1pt}
\newcommand{\tightertimes}{\hskip-3pt\times\hskip-3pt}
\newcommand\todo[1]{\ \vspace{5mm}\par \noindent\framebox{\begin{minipage}[c]{0.95 \textwidth} \tt #1\end{minipage}} \vspace{5mm} \par}
\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}

@@

\begin{abstract}
  We study the category of character sheaves on smooth commutative
  group schemes $G$ locally of finite type over finite fields
  $\mathbb{F}_q$. Assuming that the geometric component group of $G$
  is finitely-generated, we show that the group of isomorphism classes
  of character sheaves on $G$ is canonically isomorphic to the group
  of characters of $G(\mathbb{F}_q)$. We use this result to exhibit an
  isomorphism between admissible characters of $T(K)$ and isomorphism
  classes of character sheaves on the Greenberg transform of the Néron
  model of $T$, where $K$ is any non-Archimdean local field and $T$ is
  any algebraic torus over $K$.
\end{abstract}

@@

Since the character sheaves that appear in this paper are not quite an
instance of those defined by George Luzstig, who coined the term, we
begin by explaining what we mean by `character sheaves' in this
paper. Let $G$ be a smooth commutative group scheme locally of finite
type over $\Fq$ \David{I think our notation is clearer if we use $k$
  rather than $\Fq$}; $G$ need not be reductive, connected, nor of
finite type over $\Fq$. Fix a prime $\ell$ that does not divide
$q$. By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq
(\gcs{L},\mu,F)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
$\gcs{L}$ on the \'etale site of ${\bar G} \ceq G \times_{\Spec\Fq}
\Spec{\bFq}$, locally constant of rank-$1$ on every connected
component of ${\bar G}$, equipped with an isomorphism $\mu: m^*
\gcs{L} \to \gcs{L}\boxtimes \gcs{L}$, where $m : G\times G \to G$ is
the group operation for $G$, and an isomorphism $F : \Frob_{G}^*
\gcs{L} \to \gcs{L}$, where $\Frob_{G}$ is the Frobenius automorphism
on ${\bar G}$, satisfying natural compatibility conditions with $\mu$;
these compatibility conditions are explained below.

@@

The main result of this paper is a canonical isomorphism
\[
\CSiso{\textswab{T}_d} 
\iso
\Hom_{\leq d}(T(K),\EE^\times)
\] 
between the Picard group of the category of character sheaves on
$\textswab{T}_d$ and the group of characters $T(K) \to \EE^\times$ of
depth at most $d$.  Since these isomorphisms are compatible with
respect to $d$, we also .....  \Clifton{I'll come back to working on
  this when we're closer to being finished. I'd be just as happy if
  you took this cup from my lips, though.}  In particular, by
specializing to the case $T= \mathbb{G}_{\hskip-1pt\text{m},K}$ and by
choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
be), we arrive at a model for the group of quasi-characters of
$K^\times$: the monoidal category of character sheaves on the
Greenberg transform of the Neron model of
$\mathbb{G}_{\hskip-2pt\text{m},K}$.

@@

Throughout this paper, $G$ stands for a commutative group scheme,
smooth and locally of finite type over a finite field $\Fq$; we write
$m : G\tightertimes G\to G$ for the multiplication morphism. We fix an
algebraic closure $\bFq$ of $\Fq$ and write ${\bar G} $ for the
commutative group scheme, smooth and locally of finite type over
$\bFq$ obtained by base change; the multiplication morphism for
${\bar G}$ will be denoted by ${\bar m}$. Let $\Frob_{G}$
(resp. $\Frob_{G\tighttimes G}$) be the Frobenius automorphism of
${\bar G}$ (resp. ${\bar G}\tightertimes {\bar G}$).
\Clifton{I'll insert a reference to SGA where Frobenius is defined for
  a large class of schemes over finite fields.}

@@

The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
$\cs{L}\ceq (\gcs{L},\mu,F)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic
  sheaf on (the \'etale site of) ${\bar G}$, locally constant of rank
  $1$ on connected components of ${\bar G}$;

\labitem{(CS.1)}{CS.1} $\mu: {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$
  is an isomorphism of sheaves on ${\bar G}\tightertimes {\bar G}$ such that

  \[
  \xymatrix{
    {\bar m}_3^*\gcs{L} \ar[rr]^{({\bar m}\times \id)^*\mu} \ar[d]_{(\id\tightertimes {\bar m})^*\mu}
    &&  {\bar m}^*\gcs{L}\boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
    \gcs{L} \boxtimes {\bar m}^* \gcs{L} \ar[rr]
    &&  \gcs{L} \boxtimes\gcs{L} \boxtimes \gcs{L}\\
  }
  \]
  commutes, where $m_3 \ceq m\circ (m\tightertimes\id) = m\circ (\id\tighttimes m)$;

\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
  isomorphism of sheaves on ${\bar G}$ compatible with $\mu$ in the sense that

  \[
  \xymatrix{
    \Frob_{G\tighttimes G}^* {\bar m}^* \gcs{L} \ar[rr]^{\Frob_{G\tighttimes G}^*\mu}
    && \Frob_{G\tighttimes G}^*(\gcs{L}\boxtimes \gcs{L})\\
    \ar@{=}[u] {\bar m}^*  \Frob_{G}^* \gcs{L} \ar[d]_{{\bar m}^* F}
    && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
    {\bar m}^*\gcs{L} \ar[rr]^{\mu}
    && \gcs{L} \boxtimes\gcs{L}\\
  }
  \]
  commutes.
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on ${\bar G}$ such then
  \[
  \xymatrix{
  \ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'}
  & \text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
  \gcs{L} \ar[r]^{\varphi} & \gcs{L'}
  && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
  }
  \]
  both commute.
\end{enumerate}

@@

%\begin{proposition}\label{tensor}
The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal
category [insert reference] under
$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bar G})$ to
conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$
is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\CS(G)$ puts a group
structure on the set $\CSiso{G}$ of isomorphism classes in
$\CS(G)$; we refer to this as the \cdef{Picard group} of character
sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
\Clifton{Replace ncatlab with other references.}

@@

Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
determines a point ${\bar g}$ on ${\bar G}$ fixed by $\Frob_G$ and
therefore an automorphism $F_{\bar g}$ of $\gcs{L}_{\bar g}$. Note
that $\Aut_{\EE}(\gcs{L}_{\bar g}) \iso \EE^\times$, canonically (this
follows from second condition appearing in the definition of character
sheaves). The isomorphism $\mu : {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$,
defined by $g \mapsto F_{\bar g}$, is a group homomorphism;
we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank
  $1$ local system. More generally, trace is needed.}

@@

\begin{proposition}\label{prop:pullback}
  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
  $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes{\bar f})^*\mu,{\bar f}^*F)$
  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
  \[
  \xymatrix{
  \CSiso{G} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CSiso{H}\\
  \Hom_\text{grp}(G(\Fq),\EE^\times) \ar[r] & \Hom_\text{grp}(H(\Fq),\EE^\times)
  }
  \]
  is a commutative diagram of groups, where the lower homomorphism is
  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
\end{proposition}

\begin{proof}
  Let $\cs{L}$ be a character sheaf on $G$. We start by showing that
  ${\bar f}^*\gcs{L}$ is locally constant on connected components of
  ${\bar H}$. Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any
  connected component and let $i$ be the image of $j$ under the group
  homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by
  applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.
  \Clifton{Replace with a better reference, eventually.}
  Write $c_i : \bar{G}^i \hookrightarrow \bar{G}$ for
  the inclusion of $\bar{G}^i$ and ${\bar f}^j : {\bar H}^j \to {\bar G}^i$
  for the restriction of $f$ to $\bar{H}^j$.  Since $\cs{L}$
  is a character sheaf, $\gcs{L}$ is locally constant on the connect
  components of ${\bar G}$; thus, there is a finite etale covering
  $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G^i})$
  is constant. Let $b_j : Y_j \to {\bar H}^j$ be the
  pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be
  the map opposite ${\bar f}^j$. Then $b_j$ is a finite etale covering
  of ${\bar H}^j$ and
  \[
  b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)
  = ({\bar f}\circ c_j \circ b_j)^*\gcs{L}
  = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G^i}).
  \]

  Since $a_i^* (\gcs{L}\vert_{\bar G^i})$ is a constant sheaf and since the pull-back
  of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
  it follows that $b_j^* \left( ({\bar f}^*\gcs{L})\vert_{{\bar H}^j}\right)$
  is a constant sheaf. Thus, ${\bar f}^*\gcs{L}$ is locally constant on
  ${\bar H}^j$. Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every
  geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has
  rank $1$ on connected components of ${\bar G}$, it follows that
  $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$.
  This completes the proof that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.0}.

  To see that $({\bar f}\tightertimes {\bar f})^* \gcs{L}$ satisfies
  condition \ref{CS.1} simply apply the functor $({\bar f}\tightertimes {\bar f})^*$
  to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
  $({\bar f}\tightertimes {\bar f})^*(\gcs{L} \boxtimes\gcs{L}) \iso {\bar f}^*\gcs{L} \boxtimes {\bar f}^*\gcs{L}$
  (a few times). Likewise, to see that ${\bar f}^*\gcs{L}$ satisfies condition
  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
  Then use the fact that $f$ is defined over $\Fq$, so
  $({\bar f}\tightertimes {\bar f})^*\Frob_{G\tighttimes G}^* \iso \Frob_{G\tighttimes G} ({\bar f}\tightertimes {\bar f})^*$,
  and the fact that $f$ is a morphism of group schemes, so
  $({\bar f}\tightertimes {\bar f})^* {\bar m}^*\iso {\bar m}^* {\bar f}^*$
  (isomorphisms of functors on constructible sheaves).

  To see that $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes {\bar f})^*\mu,{\bar f}^*F)$
  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors ${\bar f}^*$ and
  ${\bar f}^*\tightertimes{\bar f}^*$ to \ref{CS.3} and argue as
  above. It follows from the fact that sheaf hom commutes with these
  functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.

@@

  First, observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
  sends character sheaves on $G$ to Weil local systems on
  $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
  mean a Weil sheaf on $G$ which is a local system on ${\bar G}$).
  While is it not true that all Weil local systems on $G$
  descend to sheaves on $G$, those that appear in the image of the
  forgetful functor from character sheaves do.

>>>>

\newcommand{\cdef}[1]{{{\color{cyan}#1}\index{#1}}} 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\newcommand{\GN}[1]{\textswab{#1}}
\newcommand{\bGN}[1]{{\bar{\textswab{#1}}}}
\newcommand{\TT}{\underline{T}}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\cs}[1]{{\mathcal{#1}}}
\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
\newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
\newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
\newcommand{\CSbiso}[1]{\CS_0(#1)_{/\text{iso}}}
\newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}

@@

\newcommand{\tighttimes}{\hskip-1pt\times\hskip-1pt}
\newcommand{\tightertimes}{\hskip-3pt\times\hskip-3pt}
\newcommand{\tighterboxtimes}{\hspace{-2pt}\boxtimes\hspace{-2pt}}

\renewcommand{\bf}{\bar{f}}
\newcommand{\bg}{\bar{g}}
\newcommand{\bm}{\bar{m}}
\newcommand{\bG}{\bar{G}}
\newcommand{\bH}{\bar{H}}
\newcommand{\GxG}{G \tightertimes G}
\newcommand{\bGxG}{\bar{G} \tightertimes \bar{G}}
\newcommand{\bfxf}{\bar{f} \tightertimes \bar{f}}
\newcommand{\GxxG}{G \tighttimes G}
\newcommand{\LxL}{\gcs{L} \tighterboxtimes \gcs{L}}

\newcommand\todo[1]{\ \vspace{5mm}\par \noindent\framebox{\begin{minipage}[c]{0.95 \textwidth} \tt #1\end{minipage}} \vspace{5mm} \par}
\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}

@@

\begin{abstract}
  We study the category of character sheaves on smooth commutative
  group schemes $G$ locally of finite type over finite fields
  $\Fq$. Assuming that the geometric component group of $G$
  is finitely-generated, we show that the group of isomorphism classes
  of character sheaves on $G$ is canonically isomorphic to the group
  of characters of $G(\Fq)$. We use this result to exhibit an
  isomorphism between admissible characters of $T(K)$ and isomorphism
  classes of character sheaves on the Greenberg transform of the Néron
  model of $T$, where $K$ is any non-Archimdean local field and $T$ is
  any algebraic torus over $K$.
\end{abstract}

@@

Since the character sheaves that appear in this paper are not quite an
instance of those defined by George Luzstig, who coined the term, we
begin by explaining what we mean by `character sheaves' in this
paper. Let $G$ be a smooth commutative group scheme locally of finite
type over $\Fq$ \David{I think our notation is clearer if we use $k$
  rather than $\Fq$}; $G$ need not be reductive, connected, nor of
finite type over $\Fq$. Fix a prime $\ell$ that does not divide
$q$. By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq
(\gcs{L},\mu,F)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
$\gcs{L}$ on the \'etale site of $\bG \ceq G \times_{\Spec\Fq}
\Spec{\bFq}$, locally constant of rank-$1$ on every connected
component of $\bG$, equipped with an isomorphism $\mu: m^*
\gcs{L} \to \LxL$, where $m : G\times G \to G$ is
the group operation for $G$, and an isomorphism $F : \Frob_{G}^*
\gcs{L} \to \gcs{L}$, where $\Frob_{G}$ is the Frobenius automorphism
on $\bG$, satisfying natural compatibility conditions with $\mu$;
these compatibility conditions are explained below.

@@

The main result of this paper is a canonical isomorphism
\[
\CSiso{\textswab{T}_d} 
\iso
\Hom_{< d}(T(K),\EE^\times)
\] 
between the Picard group of the category of character sheaves on
$\textswab{T}_d$ and the group of characters $T(K) \to \EE^\times$ of
depth at most $d$.  Since these isomorphisms are compatible with
respect to $d$, we also .....  \Clifton{I'll come back to working on
  this when we're closer to being finished. I'd be just as happy if
  you took this cup from my lips, though.}  In particular, by
specializing to the case $T= \Gm{K}$ and by
choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
be), we arrive at a model for the group of quasi-characters of
$K^\times$: the monoidal category of character sheaves on the
Greenberg transform of the Neron model of
$\Gm{K}$.

@@

Throughout this paper, $G$ stands for a commutative group scheme,
smooth and locally of finite type over a finite field $\Fq$; we write
$m : \GxG\to G$ for the multiplication morphism. We fix an
algebraic closure $\bFq$ of $\Fq$ and write $\bG $ for the
commutative group scheme, smooth and locally of finite type over
$\bFq$ obtained by base change; the multiplication morphism for
$\bG$ will be denoted by $\bm$. Let $\Frob_{G}$
(resp. $\Frob_{\GxxG}$) be the Frobenius automorphism of
$\bG$ (resp. $\bGxG$).
\Clifton{I'll insert a reference to SGA where Frobenius is defined for
  a large class of schemes over finite fields.}

@@

The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
$\cs{L}\ceq (\gcs{L},\mu,F)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic
  sheaf on (the \'etale site of) $\bG$, locally constant of rank
  $1$ on connected components of $\bG$;

\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
  is an isomorphism of sheaves on $\bGxG$ such that

  \[
  \xymatrix{
    \bm_3^*\gcs{L} \ar[rr]^{(\bm\times \id)^*\mu} \ar[d]_{(\id\tightertimes \bm)^*\mu}
    &&  \bm^*\LxL \ar[d]^{\mu \boxtimes \id} \\
    \gcs{L} \boxtimes \bm^* \gcs{L} \ar[rr]
    &&  \gcs{L} \boxtimes\LxL\\
  }
  \]
  commutes, where $m_3 \ceq m\circ (m\tightertimes\id) = m\circ (\id\tighttimes m)$;

\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
  isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that

  \[
  \xymatrix{
    \Frob_{\GxxG}^* \bm^* \gcs{L} \ar[rr]^{\Frob_{\GxxG}^*\mu}
    && \Frob_{\GxxG}^*(\LxL)\\
    \ar@{=}[u] \bm^*  \Frob_{G}^* \gcs{L} \ar[d]_{\bm^* F}
    && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
    \bm^*\gcs{L} \ar[rr]^{\mu}
    && \LxL\\
  }
  \]
  commutes.
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on $\bG$ such then
  \[
  \xymatrix{
  \ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'}
  & \text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
  \gcs{L} \ar[r]^{\varphi} & \gcs{L'}
  && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
  }
  \]
  both commute.
\end{enumerate}

@@

%\begin{proposition}\label{tensor}
The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal
category [insert reference] under
$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bG})$ to
conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$
is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\CS(G)$ puts a group
structure on the set $\CSiso{G}$ of isomorphism classes in
$\CS(G)$; we refer to this as the \cdef{Picard group} of character
sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
\Clifton{Replace ncatlab with other references.}

@@

Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
determines a point $\bg$ on $\bG$ fixed by $\Frob_G$ and
therefore an automorphism $F_{\bg}$ of $\gcs{L}_{\bg}$. Note
that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EE^\times$, canonically (this
follows from second condition appearing in the definition of character
sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$,
defined by $g \mapsto F_{\bg}$, is a group homomorphism;
we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank
  $1$ local system. More generally, trace is needed.}

@@

\begin{proposition}\label{prop:pullback}
  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
  $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
  \[
  \xymatrix{
  \CSiso{G} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CSiso{H}\\
  \Hom_\text{grp}(G(\Fq),\EE^\times) \ar[r] & \Hom_\text{grp}(H(\Fq),\EE^\times)
  }
  \]
  is a commutative diagram of groups, where the lower homomorphism is
  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
\end{proposition}

\begin{proof}
  Let $\cs{L}$ be a character sheaf on $G$. We start by showing that
  $\bf^*\gcs{L}$ is locally constant on connected components of
  $\bH$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
  connected component and let $i$ be the image of $j$ under the group
  homomorphism $\pi_0(\bG) \to \pi_0(\bH)$ obtained by
  applying the functor $\pi_0$ to $\bf$; see \cite{vdG&M}*{III, 3.28}, for example.
  \Clifton{Replace with a better reference, eventually.}
  Write $c_i : \bG^i \hookrightarrow \bG$ for
  the inclusion of $\bG^i$ and $\bf^j : \bH^j \to \bG^i$
  for the restriction of $f$ to $\bH^j$.  Since $\cs{L}$
  is a character sheaf, $\gcs{L}$ is locally constant on the connect
  components of $\bG$; thus, there is a finite etale covering
  $a_i : X_i \to \bG^i$ such that $a_i^* (\gcs{L}\vert_{\bG^i})$
  is constant. Let $b_j : Y_j \to \bH^j$ be the
  pull-back of $a_i$ along $\bf^j$; let $g_j : Y_j \to X_i$ be
  the map opposite $\bf^j$. Then $b_j$ is a finite etale covering
  of $\bH^j$ and
  \[
  b_j^* \left( (\bf^* \gcs{L})\vert_{\bH^j}\right)
  = (\bf\circ c_j \circ b_j)^*\gcs{L}
  = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bG^i}).
  \]

  Since $a_i^* (\gcs{L}\vert_{\bG^i})$ is a constant sheaf and since the pull-back
  of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
  it follows that $b_j^* \left( (\bf^*\gcs{L})\vert_{\bH^j}\right)$
  is a constant sheaf. Thus, $\bf^*\gcs{L}$ is locally constant on
  $\bH^j$. Since $(\bf^*\gcs{L})_{\bg} = \gcs{L}_{f(\bg)}$ for every
  geometric point ${\bg}$ on $\bG$, and since $\gcs{L}$ has
  rank $1$ on connected components of $\bG$, it follows that
  $f^*\gcs{L}$ also has rank $1$ on connected components of $\bG$.
  This completes the proof that $\bf^*\gcs{L}$ satisfies condition \ref{CS.0}.

  To see that $(\bfxf)^* \gcs{L}$ satisfies
  condition \ref{CS.1} simply apply the functor $(\bfxf)^*$
  to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \boxtimes \bf^*\gcs{L}$
  (a few times). Likewise, to see that $\bf^*\gcs{L}$ satisfies condition
  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
  Then use the fact that $f$ is defined over $\Fq$, so
  $(\bfxf)^*\Frob_{\GxxG}^* \iso \Frob_{\GxxG} (\bfxf)^*$,
  and the fact that $f$ is a morphism of group schemes, so
  $(\bfxf)^* \bm^*\iso \bm^* \bf^*$
  (isomorphisms of functors on constructible sheaves).

  To see that $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors $\bf^*$ and
  $\bf^*\tightertimes\bf^*$ to \ref{CS.3} and argue as
  above. It follows from the fact that sheaf hom commutes with these
  functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.

@@

  First, observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
  sends character sheaves on $G$ to Weil local systems on
  $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
  mean a Weil sheaf on $G$ which is a local system on $\bG$).
  While is it not true that all Weil local systems on $G$
  descend to sheaves on $G$, those that appear in the image of the
  forgetful functor from character sheaves do.

  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies
  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
  \David{Should we move this definition since it will be important elsewhere?}
  Let $b : \bG \to G$ be base change
  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
  The proof of Proposition~\ref{prop:pullback} adapts
  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
  monoidal functor. This functor is fully faithful; see
  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
  show that $b^*$ is essentially surjective.
